\documentclass[11pt, a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{caption}

\title{\textbf{Supplementary Material: Bias Correction Experiment}}
\author{Gemini Advanced}
\date{August 10, 2025}

\begin{document}

\maketitle

\section{Complete Quantitative Summary}

This table provides the full set of summary statistics for both the 1km bimodal and 9km normal scenarios. The metrics show the mean, standard deviation, and the percentage of the spatial domain where the "Pollutant X" value exceeds the 65 ppm threshold.

\begin{table}[h!]
\centering
\caption{Complete quantitative summary for all scenarios and methods.}
\label{tab:full_summary}
\resizebox{\textwidth}{!}{
\begin{tabular}{llccc}
\toprule
\textbf{Scenario} & \textbf{Method} & \textbf{Mean (ppm)} & \textbf{Std Dev (ppm)} & \textbf{\% Area > 65 ppm} \\
\midrule
\textbf{1km Bimodal} & Original & 56.04 & 5.17 & 2.69\% \\
& Stations (Observed) & 60.42 & 5.95 & 16.44\% \\
\cmidrule{2-5}
& Scaling & 58.38 & 5.38 & 15.86\% \\
& Delta Change & 58.47 & 5.17 & 14.72\% \\
& Variance Scaling & 59.01 & 3.94 & 6.41\% \\
& Parametric (Normal) & 59.01 & 3.94 & 6.41\% \\
& Parametric (Gamma) & 58.99 & 3.97 & 6.57\% \\
& Quantile Mapping & 60.74 & 4.11 & 14.88\% \\
& Spatial Delta & 58.06 & 6.96 & 17.59\% \\
\midrule
\textbf{9km Normal} & Original & 60.14 & 1.66 & 0.00\% \\
& Stations (Observed) & 60.42 & 5.95 & 16.44\% \\
\cmidrule{2-5}
& Scaling & 61.33 & 1.70 & 0.00\% \\
& Delta Change & 61.32 & 1.66 & 0.00\% \\
& Variance Scaling & 62.70 & 5.57 & 35.00\% \\
& Parametric (Normal) & 62.70 & 5.57 & 35.00\% \\
& Parametric (Gamma) & 55.64 & 28.21 & 46.00\% \\
& Quantile Mapping & 60.72 & 4.59 & 15.00\% \\
& Spatial Delta & 61.25 & 1.82 & 2.00\% \\
\bottomrule
\end{tabular}
}
\end{table}

\section{Cross-Validation Results}

This table provides the definitive ranking of the statistical methods based on their predictive skill. The Root Mean Square Error (RMSE) was calculated using a leave-one-out cross-validation approach on the 1km bimodal dataset. Lower RMSE indicates a better prediction.

\begin{table}[h!]
\centering
\caption{Leave-one-out cross-validation results for the 1km bimodal scenario.}
\label{tab:rmse}
\begin{tabular}{lc}
\toprule
\textbf{Method} & \textbf{Average RMSE} \\
\midrule
\textbf{Spatial Delta} & \textbf{5.07} \\
Original & 5.32 \\
Variance Scaling & 5.46 \\
Parametric (Normal) & 5.46 \\
Delta Change & 6.26 \\
Scaling & 6.51 \\
Parametric (Gamma) & 6.56 \\
Quantile Mapping & 8.30 \\
\bottomrule
\end{tabular}
\end{table}

\section{Mathematical Formulations of Bias Correction Methods}

Let $M_{grid}$ be the original model data on the full grid, and $M_{obs}$ be the model data extracted at the station locations. Let $O$ be the full time series of station observations, and $\bar{O}$ and $\sigma_O$ be the mean and standard deviation of the station observations, respectively.

\subsection{Delta Change}
\begin{itemize}
    \item \textbf{Concept:} Assumes the bias is a simple additive offset, constant across the entire domain.
    \item \textbf{Equation:} $M'_{grid} = M_{grid} + (\bar{O} - \bar{M}_{obs})$
\end{itemize}

\subsection{Scaling}
\begin{itemize}
    \item \textbf{Concept:} Assumes the bias is a multiplicative factor.
    \item \textbf{Equation:} $M'_{grid} = M_{grid} \times (\bar{O} / \bar{M}_{obs})$
\end{itemize}

\subsection{Variance Scaling}
\begin{itemize}
    \item \textbf{Concept:} Corrects both the mean and the variance to match the observations.
    \item \textbf{Equation:} $M'_{grid} = (M_{grid} - \bar{M}_{obs}) (\sigma_{O} / \sigma_{M_{obs}}) + \bar{O}$
\end{itemize}

\subsection{Quantile Mapping (QM)}
\begin{itemize}
    \item \textbf{Concept:} A non-parametric method that forces the model's distribution to perfectly match the observed distribution.
    \item \textbf{Equation:} $M'_{grid} = \text{CDF}_{O}^{-1} (\text{CDF}_{M_{grid}}(M_{grid}))$
\end{itemize}

\subsection{Parametric Mapping}
\begin{itemize}
    \item \textbf{Concept:} A variation of QM that assumes the data follows a specific statistical distribution.
    \item \textbf{Equation:} $M'_{grid} = \mathcal{F}_{O}^{-1} (\mathcal{F}_{M_{grid}}(M_{grid}))$ for a fitted distribution $\mathcal{F}$.
\end{itemize}

\subsection{Spatial Delta}
\begin{itemize}
    \item \textbf{Concept:} Assumes the additive bias varies spatially.
    \item \textbf{Equation:} $M'_{grid}(x,y) = M_{grid}(x,y) + \text{Interpolate}(\bar{O}_i - M_{obs,i}, x, y)$
\end{itemize}

\end{document}
